### 2024-03-13 HickernellFredSpecialSession.tex
Updates from Overleaf

Low discrepancy (LD) sequences, such as lattice, digital, and Halton sequences, can be used to estimate multivariate integrals with greater computational efficiency than independent and identically distributed (IID) sequences.  The use of LD sequences for density estimation has been less studied, but see %\cite{AbdEtal21a,LEcuyer2022b,LEcPuc20a} 
[1--3] for some recent work.

We

@@

If you would like to include references, please do so by creating a simple list numbered by [1], [2], [3], \ldots. See example below.
Please do not use the \texttt{bibliography} environment or \texttt{bibtex} files.
APA reference style is recommended.
\begin{enumerate}
	\item[{[1]}]
{Ben Abdellah}, A., L'Ecuyer, P., Owen, A.~B., and Puchhammer, F. (2021).
\newblock Density estimation by randomized quasi-{M}onte {C}arlo.
\newblock {\em SIAM/ASA J.\ Uncertain.\ Quantif.}, 9(280-301).

@@

\item[{[3]}]
L'Ecuyer, P., Puchhammer, F., and {Ben Abdellah}, A. (2022).
\newblock Monte carlo and quasi{\textendash}{M}onte {C}arlo density estimation via conditioning.
\newblock {\em INFORMS J.\ Comput.}, 34(3):1729--1748.
\end{enumerate}

Equations may be used if they are referenced. Please note that the equation numbers may be different (but will be cross-referenced correctly) in the final program book.
\end{talk}

\bibliographystyle{apalike}
\bibliography{FJH23,FJHown23}

>>>>

Low discrepancy (LD) sequences, such as lattice, digital, and Halton sequences, can be used to estimate multivariate integrals with greater computational efficiency than independent and identically distributed (IID) sequences.  The use of LD sequences for density estimation has been less studied in the past, but studied recently %\cite{AbdEtal21a,LEcuyer2022b,LEcPuc20a} 
[1--3].

This talk explores further the use of LD sequences for kernel density estimation, but from a deterministic perspective.  Given a random variable $Y = f(\boldsymbol{X})$, where $\boldsymbol{X} \sim \mathcal{U}[0,1]^d$, with a probability density $\varrho$, and kernel density estimate, $\varrho$ as

@@

\begin{enumerate}
	\item[{[1]}]
{Ben Abdellah}, A., L'Ecuyer, P., Owen, A.~B., and Puchhammer, F. (2021).
\newblock Density estimation by randomized quasi-{M}onte {C}arlo.
\newblock {\em SIAM/ASA J.\ Uncertain.\ Quantif.}, 9(280-301).

@@

\item[{[3]}]
L'Ecuyer, P., Puchhammer, F., and {Ben Abdellah}, A. (2022).
\newblock Monte Carlo and quasi{\textendash}{M}onte {C}arlo density estimation via conditioning.
\newblock {\em INFORMS J.\ Comput.}, 34(3):1729--1748.
\end{enumerate}

\end{talk}

%\bibliographystyle{apalike}
%\bibliography{FJH23,FJHown23}
